Kronos \& Krios: TBD

### 2017-05-22 paper/ms.tex
add text on other studies (wip)

% define macros for text
\newcommand{\project}[1]{\textsl{#1}}
\newcommand{\acronym}[1]{{\small{#1}}}
\newcommand{\gaia}{\project{Gaia}}
\newcommand{\rave}{\project{\acronym{RAVE}}}
\newcommand{\apogee}{\project{\acronym{APOGEE}}}
\newcommand{\tmass}{\project{\acronym{2MASS}}}
\newcommand{\documentname}{Article}
\newcommand{\sectionname}{Section}
\newcommand{\figname}{Figure}
\newcommand{\eqname}{Equation}
\newcommand{\dr}{\acronym{DR1}}
\newcommand{\tgas}{\acronym{TGAS}}
\newcommand{\etal}{\textit{et al}.}
\newcommand*\elem[1]{\ensuremath{\mathrm{#1}}}
\newcommand*\elemH[1]{\ensuremath{[\mathrm{#1}/\elem{H}]}}
\newcommand*{\feh}{\ensuremath{\elemH{Fe}}}
\newcommand{\sunanalog}{\text{Krios}}
\newcommand{\bizarreone}{\text{Kronos}}
\newcommand{\Tcondens}{\ensuremath{T_C}}
\newcommand{\mearth}{\ensuremath{M_\oplus}}
\newcommand{\mjupiter}{\ensuremath{M_\mathrm{Jup}}}

@@

None of the above scenarios is satisfactory as they offer no
insight on the peculiarity of the abundances of \bizarreone
(see \sectionname~{\ref{sec:data}}).
In case that the pair formed from a exchange scattering event,
we would expect the pair to be composed of typical field stars.
The unlikeliness of the above possibilities naturally leads us to
consider the alternative.
What can selectively enrich refractory (high $T_C$) elements
in one of the two stars that are born together?

@@

\citealt{Mack:2014aa} studied HD~20782/20781, two common proper motion G dwarf stars (G2/G9.5)
with a projected separation of $\sim9000$~AU (correspoding to 4.2~arcmin sky separation).
Both stars in this system host close-in giant planets.
HD~20782 hosts a Jupiter-mass planet on a very eccentric ($e\approx 0.97$) orbit with a
pericenter distance of 1.4~AU while HD~20781 hosts two Neptune-mass planets within 0.3~AU
with moderately high eccentricity ($e\sim0.1-0.3$).
They found that the abundances of 15 elements between the two stars are consistent with each other.
However, they argued that there is a moderately significant ($\sim 2\sigma$)
positive slope of $\approx 10^{-5}$~dex\,K$^{-1}$ in abundance of each star
{\it individually} with increasing \Tcondens\ for $\Tcondens>900$~K elements
(namely, Na, Mn, Cr, Si, Fe, Mg, Co, Ni, V, Ca, Ti, Al, Sc leaving out C and O
of their measurements).
They interpreted that this slope may be evidence for accretion of $10-20$~\mearth\ of 
H-depleted rocky material that were pushed in during giant planet migration.

\citealt{Teske:2016aa} studied WASP-94A/WASP-94B, a pair of F8 and F9 stars
with super-solar metallicity ($\feh\approx 0.3$ for both stars). Both stars
host a hot Jupiter.
The planet hosted by WASP-94A is transiting with a misaligned, probably
retrograde circular ($e<0.13$) orbit, while that hosted by WASP-94B is a little
more massive by $\sim 0.15$~\mjupiter\ and closer in, aligned with the host
star.
With a claimed precision of $0.006$~dex (median among all elements), they
detected a depletion of volatile and moderately volatile ($\Tcondens < 1200$~K)
elements at $0.02$~dex level and an enhancement in refractory ($\Tcondens >
1200$~K) elements at $0.01$~dex level in WASP-94A relative to WASP-94B.
Excluding K, which is based on one strong line and largely affected by non-LTE
effect, their analysis shows a statistically significant non-zero slope between
$\Delta\elemH{X}$ and $\Tcondens$\footnote{Note that the condensation
  temperature $\Tcondens$ used is for solar (system? atmosphere?) composition
  gas, which can differ from that of higher metallicity gas.}.
They considered multiple possibilities related to the formation and evolution
of planetary systems around each star as well as causes unrelated to planets
such as dust cleansing during the fully convective phase or different rotation
and granulation between the stars, but did not favor any particular one.

The pair of G5 stars HD 80606/HD 80607 has been independently studied by
\citealt{Saffe:2015aa} and \citealt{Mack:2016aa} using the same KECK HIRES
spectra. HD 80606 hosts a giant planet with mass of $4~\mjupiter$ at $0.5$~AU
on a very eccentric ($e\approx0.95$) orbit while HD 80607 has no detected
planets.
Both stars are super solar with $\feh=0.35$.

>>>>

% define macros for text
\newcommand{\project}[1]{\textsl{#1}}
\newcommand{\acronym}[1]{{\small{#1}}}
\newcommand{\gaia}{\project{Gaia}}
\newcommand{\rave}{\project{\acronym{RAVE}}}
\newcommand{\apogee}{\project{\acronym{APOGEE}}}
\newcommand{\tmass}{\project{\acronym{2MASS}}}
\newcommand{\documentname}{Article}
\newcommand{\sectionname}{Section}
\newcommand{\figname}{Figure}
\newcommand{\eqname}{Equation}
\newcommand{\dr}{\acronym{DR1}}
\newcommand{\tgas}{\acronym{TGAS}}
\newcommand{\etal}{\textit{et al}.}
\newcommand*\elem[1]{\ensuremath{\mathrm{#1}}}
\newcommand*\elemH[1]{\ensuremath{[\mathrm{#1}/\elem{H}]}}
\newcommand*\teff{\ensuremath{T_\mathrm{eff}}}
\newcommand*\logg{\ensuremath{\log{g}}}
\newcommand*{\feh}{\ensuremath{\elemH{Fe}}}
\newcommand{\sunanalog}{\text{Krios}}
\newcommand{\bizarreone}{\text{Kronos}}
\newcommand{\Tcondens}{\ensuremath{T_C}}
\newcommand{\mearth}{\ensuremath{M_\oplus}}
\newcommand{\mjupiter}{\ensuremath{M_\mathrm{Jup}}}

@@

None of the above scenarios is satisfactory as they offer no
insight on the peculiarity of the abundances of \bizarreone\
(see \sectionname~{\ref{sec:data}}).
In case that the pair formed from a exchange scattering event,
we would expect the pair to be composed of typical field stars.
The unlikeliness of the above possibilities naturally leads us to
consider the alternative.
What can selectively enrich refractory (high $T_C$) elements
in one of the two stars that are born together?

@@

\input{otherstudies.tex}

We summarize the few wide separation common proper motion pairs that have been
studied in detailed chemical abundance so far.
These systems are HD~20782/HD~20781, HD~80606/HD~80607, XO-2N/XO-2S, HAT-P-1,
WASP-94A/WASP94-B, and HD~133131A/HD~133131B.
Main properties of the systems relevant to the present discussion are
summarized in \tablename~\ref{tab:otherstudies}.
Their reported abundance differences $\Delta\elemH{X}$ where the difference is
always taken as $\mathrm{higher}~\feh - \mathrm{lower}~\feh$ are plotted in
\figname~\ref{fig:relabun_tcrank} as a function of \Tcondens-rank for
comparision with this pair.

{\bf HD~20782/HD~20782:} 
\citealt{Mack:2014aa} studied HD~20782/20781, two common proper motion G dwarf stars (G2/G9.5)
with a projected separation of $\sim9000$~AU (correspoding to 4.2~arcmin sky separation).
Both stars in this system host close-in giant planets.
HD~20782 hosts a Jupiter-mass planet on a very eccentric ($e\approx 0.97$) orbit with a
pericenter distance of 1.4~AU while HD~20781 hosts two Neptune-mass planets within 0.3~AU
with moderately high eccentricity ($e\sim0.1-0.3$).
They found that the abundances of 15 elements between the two stars are consistent with each other.
However, they argued that there is a moderately significant ($\sim 2\sigma$)
positive slope of $\approx 10^{-5}$~dex\,K$^{-1}$ in abundance of each star
{\it individually} with increasing \Tcondens\ for $\Tcondens>900$~K elements
(namely, Na, Mn, Cr, Si, Fe, Mg, Co, Ni, V, Ca, Ti, Al, Sc leaving out C and O
of their measurements).
They interpreted that this slope may be evidence for accretion of $10-20$~\mearth\ of 
H-depleted rocky material that were pushed in during giant planet migration.

{\bf WASP-94A/WASP-94B:} 
\citealt{Teske:2016aa} studied WASP-94A/WASP-94B, a pair of F8 and F9 stars
with super-solar metallicity ($\feh\approx 0.3$ for both stars). Both stars
host a hot Jupiter.
The planet hosted by WASP-94A is transiting with a misaligned, probably
retrograde circular ($e<0.13$) orbit, while that hosted by WASP-94B is a little
more massive by $\sim 0.15$~\mjupiter\ and closer in, aligned with the host
star.
With a claimed precision of $0.006$~dex (median among all elements), they
detected a depletion of volatile and moderately volatile ($\Tcondens < 1200$~K)
elements at $0.02$~dex level and an enhancement in refractory ($\Tcondens >
1200$~K) elements at $0.01$~dex level in WASP-94A relative to WASP-94B.
Excluding K, which is based on one strong line and largely affected by non-LTE
effect, their analysis shows a statistically significant non-zero slope between
$\Delta\elemH{X}$ and $\Tcondens$\footnote{Note that the condensation
  temperature $\Tcondens$ used is for solar (system? atmosphere?) composition
  gas, which can differ from that of higher metallicity gas.}.
They considered multiple possibilities related to the formation and evolution
of planetary systems around each star as well as causes unrelated to planets
such as dust cleansing during the fully convective phase or different rotation
and granulation between the stars, but did not favor any particular one.

{\bf HD~80606/HD~80607:}
The pair of G5 stars HD 80606/HD 80607 has been independently studied by
\citealt{Saffe:2015aa} and \citealt{Mack:2016aa} using the same KECK HIRES
spectra. HD 80606 hosts a giant planet with mass of $4~\mjupiter$ at $0.5$~AU
on a very eccentric ($e\approx0.95$) orbit while HD 80607 has no detected
planets.
Both stars are super solar with $\feh=0.35$.

{\bf HAT-P-1:}
HAT-P-1 is a pair of G0 stars separated 11\farcs apart in sky
with $\feh\approx0.15$.
The secondary star in the system is known to host one transiting giant planet
while no planet has been discovered around the primary star.
\citealt{Liu:2014aa} found that the two stars are identical in their atmospheric composition:
\feh\ is $0.146 \pm 0.014$ and $0.155 \pm 0.007$ for the primary and secondary respectively,
and $\Delta\elem{X}/{Fe}$ is consistent with zero for 23 elements measured
with the mean error being $0.013$~dex.
Based on this analysis, they concluded that the presence of close-in giant planet
does not necessarily lead to stellar atmospheric pollution of the host star.

{\bf XO-2N/XO-2S:}
The double star system XO-2 has received much attention due to
possibly the most robust and significant difference between the component stars
among those so far studied.
XO-2 is a pair of G9 stars with super-solar metallicity ($\feh \gtrsim 0.35$),
each hosting planet(s).
XO-2N hosts on giant planet while XO-2S is known to host two giant planets with
masses $0.26 \mjupiter$ and $1.37 \mjupiter$ on moderately eccentric ($\approx
0.15$) orbits at $<0.5$~AU.

The system was first analyzed by \citealt{Teske:2013aa}, who examined and found
essentially no significant difference in Fe, Ni, C, and O between the two
stars.
However, re-analysis of the system using the same data in
\citealt{Teske:2015aa} found that the trend of $\Delta\elemH{X}$ with
\Tcondens\ varies significantly depending on the stellar parameters chosen in
their analysis. Both analyses were based on spectra
using Subaru High Dispersion Spectrograph at spectral resolution $R=60000$
covering $4450-5660~\AA$ and $5860-7100~\AA$ with S/N of $170-230$
(\citealt{Teske:2013aa}).

Independently, \citealt{Ramirez:2015aa} used Keck HIRES spectra ($R=67000$,
$4080-8300~\AA$) of the component stars with S/N of $350$ (in $5000-7500~\AA$)
to perform a differential abundance analysis.
They find that all 23 elements including Fe is enhanced in XO-2N
compared to XO-2S, and that the difference $\Delta\elemH{X}$ shows
a significant correlation with \Tcondens.
At low \Tcondens, volatile elements differ by $0.015$~dex
while the range of difference spans upto $0.1$~dex at $\Tcondens>1600$~K.
There are inconsistencies in the determination of stellar parameters
(\teff\ and \logg) between spectroscopic (based on Fe I/II lines)
and photometric analysis,
but the existence of correlation between $\Delta\elem{H}$ and
\Tcondens\ seems robust.

\citealt{Ramirez:2015aa} argued that the {\it depletion} of
volatile elements in XO-2S relative to XO-2N is plausibly
due to {\it more} gas giant planets around XO-2S,
following a similar interpretation of \citealt{Melendez:2009aa}
on the trend between solar twins and the Sun.
In this scenario, forming planets in the protoplanetary disk
are supposed to ``lock'' heavier elements to the core of gas giant
planets as well as some volatile elements in their envelopes.
Then, the host star will somehow accrete {\it gas} depleted in
metals compared to their protostellar condition.
By tuning the metal content ($Z/X$) of gas giant planets
and when the accretion of gas occurs in terms of how much mass
is in the convective envelop then, they can match
the mass difference of gas giant planets around each star,
which is at least $1~\mjupiter$.
For the positive correlation of $\Delta\elemH{X}$ with \Tcondens,
\citealt{Ramirez:2015aa} estimated that $20~\mearth$
of equal-part mixture of Earth and CM chondrite-like material
can explain the trend either as
refractory {\it depletion} in XO-2S due to {\it more} rocky planets
around XO-2S, or refractory enhancement in XO-2N by late time accretion
in which case the complete opposite would be true.

Finally, \citealt{Biazzo:2015aa}

% Useful follow up efforts
